Acceleration of Derivative Calculations with Application to Radial Basis Function -- Finite-Differences on the Intel MIC Architecture

### 2014-01-16 acm/RBF_Section.tex
small correction in RBF section.

To obtain a RBF derivative approximation at a node location that will result in a sparse differentiation matrix (DM), the RBF-FD method has been developed over the last decade \cite{TAI1,TAI2,SDY02,WrFo06}. RBF-FD is conceptually similar to standard finite differences (FD). However, the differentiation weights for approximating a derivative at a given node (forming one row of the RBF-FD derivative matrix) are derived from a function approxiation within the stencil formed by a linear combination of RBFs centered at the different points of the stencil. In general, $n<<N$. 
%that the linear combination of function values at the $n$ nearest node locations (a stencil) with $n \in N$ be exact for RBFs centered at each of the $n$ nodes rather than polynomials. 
The resulting derivative matrix (DM) is sparse matrix with $nN$ nonzero entries. As in FD methods, the order of the method increases with stencil size. An illustration of an RBF 32 node stencil on a sphere,  is given in Figure \ref{fig:stencil}.

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{figures/RBFStencil_n32_a}\label{fig:stencil}
\caption{An example of an RBF-FD stencil of size $n=32$ on a sphere of $N=1024$ nodes to approximate any derivative operator at the point in the square. In nonsparse format, the DM  is $1024\times1024$ with 21 nonzero entries per row.}
\end{figure}

>>>>

To obtain a RBF derivative approximation at a node location that will result in a sparse differentiation matrix (DM), the RBF-FD method has been developed over the last decade \cite{TAI1,TAI2,SDY02,WrFo06}. RBF-FD is conceptually similar to standard finite differences (FD). 
However, the differentiation weights for approximating a derivative at a given node (forming one row of the RBF-FD derivative matrix (DM)) enforce that the linear combination of function values at the $n << N$ nearest node locations (a stencil) be exact for RBFs centered at each of the $n$ nodes rather than polynomials. The result is a sparse matrix with only $n$ entries in each of its $N$ rows, resulting in a total of $nN$ nonzero entries.

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{figures/RBFStencil_n32_a}\label{fig:stencil}
\caption{An example of an RBF-FD stencil of size $n=32$ on a sphere of $N=1024$ nodes to approximate any derivative operator at the point in the square. In nonsparse format, the DM  is $1024\times1024$ with 32 nonzero entries per row.}
\end{figure}
